---
title: "Sri Lanka Child Statistics"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---



```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tsibble)
library(fabletools)
library(feasts)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(showtext)
library(sugrrants)
library(plotly)
library(scales)
library(openxlsx)
library(ceylon)
library(sp)
library(viridis)
library(sf)
population <- read.xlsx("population.xlsx")
births<-read.xlsx('births.xlsx')
infant_mortality<-read.xlsx('infant_mortality.xlsx')
arrivals<-read.xlsx('arrivals.xlsx')
departure<-read.xlsx('departure.xlsx')
enrollment<-read.xlsx('enrollment.xlsx')
infants<-read.xlsx('infants.xlsx')
children<-read.xlsx('1-2_years.xlsx')
theme_set(theme_bw())
```


# Child Population

## Column {data-width="150"}

### Child Population from 2021 to 2024

```{r}


ts.population<-as_tsibble(population,index=Year)


p1<-ggplot(ts.population,aes(x=Year,y=Child_Population))+geom_line(col="#58508d")+geom_point(col="red")+scale_x_continuous(breaks = seq(min(ts.population$Year),
                                                                                                                max(ts.population$Year),
                                                                                                                2))+labs(y="Child Population in 1000")

ggplotly(p1)       
```

### Child Arrivals to Sri Lanka (2015–2021)
```{r}
ts.arrivals<-pivot_longer(arrivals,2:4,names_to = "Group",values_to = "No_of_arrivals")
ts.arrivals$Year<-as.Date((paste0(ts.arrivals$Year, "-01-01")))

ts.arrivals<-as_tsibble(ts.arrivals,key=Group,index=Year)
p5<-ggplot(ts.arrivals,aes(x=Year,y=No_of_arrivals,col=Group))+geom_point()+geom_line()+scale_x_date(date_breaks = "1 year", date_labels = "%Y")+labs(y="No of Arrivals")+scale_color_manual(values=c("#bc5090","#003f5c","#ffa600"))
ggplotly(p5)


```

## Column {data-width="150"}

### Live Births registered from 2015 to 2021
```{r}
ts.births<-pivot_longer(births,2:4,names_to = "Group",values_to = "No_of_Births")
ts.births<-as_tsibble(ts.births,key=Group,index=Year)
ts.births$Year<-as.Date((paste0(ts.births$Year, "-01-01")))

p2<-ggplot(ts.births,aes(x=Year,y=No_of_Births,col=Group))+geom_point()+geom_line()+scale_y_continuous(labels = scales::label_number(),breaks = seq(100000,400000,50000)) +labs(y="No of Live Births")+scale_color_manual(values=c("#bc5090","#003f5c","#ffa600"))+scale_x_date(date_breaks = "1 year", date_labels = "%Y")    
                                                                                                          
ggplotly(p2)

```

### Departure of children from Sri lanka (2015-2021)

```{r}
ts.departures<-pivot_longer(departure,2:4,names_to = "Group",values_to = "No_of_Departures")
ts.departures$Year<-as.Date((paste0(ts.departures$Year, "-01-01")))
ts.departures<-as_tsibble(ts.departures,key=Group,index=Year)
p6<-ggplot(ts.departures,aes(x=Year,y=No_of_Departures,col=Group))+geom_point()+geom_line()+scale_x_date(date_breaks = "1 year", date_labels = "%Y")+labs(y="No of Departures")+scale_color_manual(values=c("#bc5090","#003f5c","#ffa600"))
ggplotly(p6)
```
## Column {data-width="150"}
### Infant Deaths per 1000 births(Infant Mortality Rate) from 2010 to 2020
```{r}
ts.deaths<-pivot_longer(infant_mortality,2:4,names_to = "Group",values_to = "Infant_Deaths")
ts.deaths<-as_tsibble(ts.deaths,key=Group,index=Year)
ts.deaths$Year<-as.Date((paste0(ts.deaths$Year, "-01-01")))

p3<-ggplot(ts.deaths,aes(x=Year,y=Infant_Deaths,col=Group))+geom_point()+geom_line()+labs(y="Infant Mortality Rate ") +scale_color_manual(values=c("#bc5090","#003f5c","#ffa600"))+scale_x_date(date_breaks = "2 years", date_labels = "%Y")
ggplotly(p3)
```

### Arrivals and Departures of children from 2015 to 2021
```{r}
arrivals$arrivals<-arrivals$Total
departure$departures<-departure$Total
df<-inner_join(arrivals,departure,by="Year")
df1<-select(df,Year,arrivals,departures)
ts.departures2<-pivot_longer(df1,2:3,names_to = "Group",values_to = "No_of_cases")
p7<-ggplot(ts.departures2,aes(x=Year,y=No_of_cases , fill=Group))+geom_col(position = "dodge")+scale_x_continuous(breaks = seq(min(ts.departures2$Year),
                                                                                                                                max(ts.departures2$Year),
                                                                                                                                 1))+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+labs(y="No of Departures/Arrivals")+scale_fill_manual(values=c("#7a5195","#ef5675"))
ggplotly(p7)

```
# Child Education

## Column {data-width="200"}
 
### Spatial Distribution of Government School student enrollment in Year 2020
```{r}
data(sf_sl_0)


new_df <- left_join(district, enrollment, by = "DISTRICT")
p8<-ggplot(data=new_df) +
  geom_sf(aes(fill=School_enrollment))+scale_fill_continuous(
    labels = label_number(big.mark = ","),
    breaks = seq(30000, 360000, 50000)
  )
ggplotly(p8)
```

## Column {data-width="200"}
### Spatial Distribution of Pre School student enrollment in Year 2021
```{r}
p9<-ggplot(data=new_df,aes(fill=)) +
  geom_sf(aes(fill=Pre_school_enrollment))
ggplotly(p9)
```

# Child Health and Nutrition

## Column{data-width="200"}
### Nutritional status of infants from 2015 to 2021 
```{r}
ts.infants<-pivot_longer(infants,2:4,names_to = "Nutritional status",values_to = "Percentage")
ts.infants<-as_tsibble(ts.infants,key=`Nutritional status`,index=Year)
p10<-ggplot(ts.infants,aes(x=Year,y=Percentage,col=`Nutritional status`))+geom_point()+geom_line()+scale_x_continuous(breaks = seq(min(ts.infants$Year),
                                                                                                                max(ts.infants$Year),
                                                                                                                1))+scale_color_manual(values=c("#003f5c","#bc5090","#ffa600"))
ggplotly(p10)
```

## Column{data-width="200"}
### Nutritional status of 1-2 years children from 2015 to 2021
```{r}
ts.children<-pivot_longer(children,2:4,names_to = "Nutritional status",values_to = "Percentage")
ts.children<-as_tsibble(ts.children,key=`Nutritional status`,index=Year)
p11<-ggplot(ts.children,aes(x=Year,y=Percentage,col=`Nutritional status`))+geom_point()+geom_line()+scale_x_continuous(breaks = seq(min(ts.children$Year),
                                                                                                                max(ts.children$Year),
                                                                                                                1))+scale_color_manual(values=c("#003f5c","#bc5090","#ffa600"))
ggplotly(p11)
```